Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-05 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

>>>>

Recall we model the idea of the finite precision measurement as IVPM.
Since the Born rule is the rule to compute the probability providing
infinity measurement resource, it would be nature to ask whether quantum
IVPM would approach the Born rule if we increase the measurement resource.
In order to understand this question, it is instructive to consider
the non-Born real-valued probability measure when $d=2$.

\begin{example}[One-qubit quantum probability measure]Consider a
quantum probability measure~$\mu:\events\rightarrow[0,1]$ defined
as follow: 
\[
\mu(P)=\begin{cases}
\mu_{\ket{\ps}}^{B}(P) & \textrm{, if }P=\proj{\ps}\textrm{ or }\proj{\ms}\textrm{ ;}\\
\mu_{\ket{0}}^{B}(P) & \textrm{, otherwise.}
\end{cases}
\]
Notice that $\mu$ is consistent with the Born rule, but computed
according to different states when applying on different projectors.\qed\end{example}

\newpage{}
